---
title: "PSTAT 10: Worksheet 4"
subtitle: "YOUR LAST NAME, YOUR FIRST NAME: YOUR NETID"
author: "Collaborated with: LAST NAME, FIRST NAME, NETID of any collaboraters"
date: "Make sure you show your work to your TA once complete."
output:
  html_document:
    theme: readable
    toc: yes
fontsize: 12pt
params:
  solution: TRUE
  release: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = F}
bfcolor <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{\\textbf{%s}}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'><b>%s</b></span>", color, x)
  } else x
}
```

Work in groups of at most 3 assigned by your TA. Take turns to explain each exercise to your group mates before proceeding to the next exercise as a group. 

---

# Exercise 0: YAML

Update the YAML to reflect your own information (i.e. name, collaborators, etc.). If you did not collaborate with anyone, note that down in the YAML. 

---

# Exercise 1: List

```{r}
y_list <- list(a = 5, b = 1:3, c = "hello")
```

**(a)** Print the list

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```



**(b)** What type of object is stored as the second member in the list?

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```





**(c)** Extract the second item of the list using index.

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```



**(d)** Extract the second item in the list using name

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```



**(e)** Add 5 to every element of the second item in the list using [[ and store the result as result_d. 

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```




**(f)** **Optional** Update "hello" to "Hey there!"

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```

---

# Exercise 2: Data frame basics


Consider three vectors:
```{r}
v1 = c(3:7)
v2 = c("orange", "purple", "blue", "white", "yellow")
v3 = c(F, T, T, F, T)
```


**(a)** Construct a data frame `df1` from the three vectors `v1, v2, v3`

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```





**(b)** Check that the object you created is a data frame.

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```




**(c)** How many rows does `df1` have

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```



**(d)** Add row names "r1", "r2" and so on

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```






**(e)** Extract the second column by index.

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```



**(f)** Extract the second column by column name.

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```


**(g)** Extract all data except the second column.

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```


**(h)** **OPTIONAL** Sort the 2nd column. Describe the sort order. 

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```


# Exercise 3: Special values!

**(a)** Write code that produces `-Inf`

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```



**(b)** Test if `NaN` is a numeric value. _Recall: `is.datatype()` functions

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```



**(c)** Give an example of an expression that results in `NaN` value and store your result as `test_nan`

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```



**(d)** **(OPTIONAL)**

```{r}
wood_chucker <- "How much wood would a wood chuck chuck if a wood chuck could chuck wood?"
```

Replace the first occurrence of chuck with `check`

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```




**(e)** **(OPTIONAL)** Replace all occurrences of chuck with `check`

`r bfcolor("Solutions:", "blue")`

```{r}
# Write your code here

```



---

# Last exercise : Learning Gains

Please remember to fill out these learning gains before showing your TA your work to get Worksheet credit!

-   Gain 1
-   Gain 2
-   Gain 3
